---
title: "SARS_CoV_2_structure_analysis"
author: "Aleksandr Kovalenko"
date: '2023-07-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Comparison of high probability residue proportion in intact and randomised structures

```{r}
prop.test(c(2020, 7236), c(3090, 9270))
prop.test(c(1922, 6952), c(2916, 8748))
prop.test(c(2316, 7930), c(3294, 9882))
```

## Proportion of residues with high probability by state

**That's how it looks with simple ANOVA:**
Load data by state only:
```{r}
prop_data <- read.csv2("data/proportion_of_high_probability_residues_by_state.csv",
                       header=T, sep=",", stringsAsFactors = T)
prop_data$proportion <- as.numeric(as.character(prop_data$proportion))
```

Perform ANOVA:
```{r}
summary(aov(proportion~state, data=prop_data))
```

```{r}
summary.lm(aov(proportion~state, data=prop_data))
```

```{r}
plot(aov(proportion~state, data=prop_data))
```

**Now a more correct analysis using generalised linear model with binomial errors:**

```{r}
prop_data <- read.csv2("data/high_probability_residues_by_state.csv",
                       header=T, sep=",", stringsAsFactors = T)
y <- cbind(prop_data$high_prob, prop_data$all_res - prop_data$high_prob)
```

```{r}
model <- glm(y~prop_data$state, quasibinomial)
summary(model)
```
## Test the influence of residue involvement into pocket and the PM prediction

```{r}
vol_data <- read.csv2("data/pocket_volume_vs_PM_probability_by_state.csv",
                       header=T, sep=",", stringsAsFactors = T)
vol_data$volume <- as.numeric(as.character(vol_data$volume))
vol_data$av_probability <- as.numeric(as.character(vol_data$av_probability))
```

(Interaction appears insignificant, si the final fit is without it)
```{r}
model <- lm(vol_data$av_probability~vol_data$state+vol_data$volume)
summary(aov(model))
```
```{r}
summary.lm(model)
```

## Analyse differences between probabilities in different structures

```{r}
prob_data <- read.csv2("data/MM_probabilities.csv",
                       header=T, sep=",", stringsAsFactors = T)
prob_data$probability <- as.numeric(as.character(prob_data$probability))

summary.lm(aov(probability~state, data=prob_data))
```

```{r}
prob_data <- read.csv2("data/LA_probabilities.csv",
                       header=T, sep=",", stringsAsFactors = T)
prob_data$probability <- as.numeric(as.character(prob_data$probability))

summary.lm(aov(probability~state, data=prob_data))
```
ANCOVA for LA residue probabilities and pocket volumes 
```{r}
prob_data <- read.csv2("data/LA_probabilities_vs_volume.csv",
                       header=T, sep=",", stringsAsFactors = T)
prob_data$probability <- as.numeric(as.character(prob_data$probability))
prob_data$volume <- as.numeric(as.character(prob_data$volume))

model <- lm(prob_data$probability~prob_data$state*prob_data$volume)
summary(aov(model))
```

```{r}
summary.lm(model)
```

```{r}
prob_data <- read.csv2("data/PS_probabilities.csv",
                       header=T, sep=",", stringsAsFactors = T)
prob_data$probability <- as.numeric(as.character(prob_data$probability))

summary.lm(aov(probability~state, data=prob_data))
```


```{r}
prob_data <- read.csv2("data/PS_probabilities_vs_volume.csv",
                       header=T, sep=",", stringsAsFactors = T)
prob_data$probability <- as.numeric(as.character(prob_data$probability))
prob_data$volume <- as.numeric(as.character(prob_data$volume))

model <- lm(prob_data$probability~prob_data$state*prob_data$volume)
summary(aov(model))
```

```{r}
summary.lm(model)
```